### 2018-01-22 mcmc.tex
typo

\paragraph{Gibbs}
Neither \MH\ \MCMC\ nor most ensemble methods good at going to very
  large numbers of parameters.\footnote{See the excellent rant ``Ensemble Methods are Doomed to Fail in High Dimensions'' at \url{http://andrewgelman.com/2017/03/15/ensemble-methods-doomed-fail-high-dimensions/}.}
Even dozens of parameters can be enough to drive autocorrelation times
  extremely large.
With larger numbers of parameters, new methods need to be considered.
Gibbs sampling is worth considering when the number of parameters is
  large, and the different parameters have different ``scopes'' in the problem.

>>>>

\paragraph{Gibbs}
Neither \MH\ \MCMC\ nor most ensemble methods are good at going to very
  large numbers of parameters.\note{See the excellent rant ``Ensemble Methods are Doomed to Fail in High Dimensions'' at \url{http://andrewgelman.com/2017/03/15/ensemble-methods-doomed-fail-high-dimensions/}.}
Even dozens of parameters can be enough to drive autocorrelation times
  extremely large.
With larger numbers of parameters, new methods need to be considered.
Gibbs sampling is worth considering when the number of parameters is
  large, and the different parameters have different ``scopes'' in the problem.
